Quantum Semiprime Factorization: Leveraging Grover's Algorithm for Efficient Prime Decomposition

### 2025-03-03 LaTeX/paper.tex
Fin.

  The typical approach to semiprime factoring on a quantum computer is 
  with Shor's algorithm, but there are many drawbacks to this approach,
  and has not yet been observed to be practically advantageous.

@@

  % Operations can be performed on a set of input registers that start in uniform 
  % superposition, and these operations will affect each potential state individually. 
  % The properties of superposition are utilized by Grover's Oracle to selectively 
  % modify the states $|x,y\rangle$ in the input registers $R_x$ and $R_y$,
  % marking them as valid by setting them to $-|x,y\rangle$, only when the output register
  % $R_z$ matches some known search term $z$. An outline of a quantum circuit for
  % Grover's algorithm is seen in Figure~\ref{fig:FIGURA1}.
  %
  The oracle in Grover's algorithm performs a controlled operation which is meant
  to differentiate states $-|x,y\rangle$ that do result in the wanted target $z$ from 
  states $|x,y\rangle$ that do not result in the target $|z\rangle$.

@@

What have we learned so far, what does it mean, at what problem scale might
we see quantum advantage based on our results, etc.

@@

\section*{Acknowledgments}  
% This section is not numbered.
% 
Jacob Collins has been funded by Chico State Enterprises as an undergraduate research assistant
through funding provided by the Department of Energy via a grant titled: \textit{QIST in the CSU:\ 
Expanding Access to Quantum Information Science and Technology.}

>>>>

  % The typical approach to semiprime factoring on a quantum computer is 
  % with Shor's algorithm, but there are many drawbacks to this approach,
  % and has not yet been observed to be practically advantageous.

@@

  % Operations can be performed on a set of input registers that start in uniform 
  % superposition, and these operations will affect each potential state individually. 
  % The properties of superposition are utilized by Grover's Oracle to selectively 
  % modify the states $|x,y\rangle$ in the input registers $R_x$ and $R_y$,
  % marking them as valid by setting them to $-|x,y\rangle$, only when the output register
  % $R_z$ matches some known search term $z$. An outline of a quantum circuit for
  % Grover's algorithm is seen in Figure~\ref{fig:FIGURA1}.

  This use of Grover's algorithm involves three main parts: some function with
  one or multiple inputs, the oracle which filters for states in which the
  desired output was observed, and the diffuser, which increases the probability 
  of observing inputs from the correct state. An overview of this circuit is
  shown in Figure~\ref{fig:FIGURA1}.

  The oracle in Grover's algorithm performs a controlled operation which is meant
  to differentiate states $-|x,y\rangle$ that do result in the wanted target $z$ from 
  states $|x,y\rangle$ that do not result in the target $|z\rangle$.

@@

Grover's algorithm has been demonstrated to be a highly versatile function,
able to invert almost any function that can be implemented on a quantum 
computer with inputs in superposition.

Quantum methods of SP factoring have been developing at a quick pace,
and it will most likely not be very long before practical examples
of quantum advantage may be seen.

@@

\section*{Acknowledgments}  
% This section is not numbered.
% 
Jacob Collins has been funded by Chico State Enterprises as an undergraduate research assistant
through funding provided by the Department of Energy via a grant titled: \emph{QIST in the CSU:\ 
Expanding Access to Quantum Information Science and Technology.}
